Changes in accessibility to foodbanks during COVID-19 and implications for the food security of vulnerable populations in Hamilton, Ontario

### 2021-04-22 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton.Rmd
First chunks of code transferred to manuscript: package installation and loading, and loading data

>>>>

```{r install-data-package, include = FALSE}
# Run only once if needed to install data package `sobiEquity`
if (!require("foodbanksHamilton", character.only = TRUE)) {
      devtools::install_github("https://github.com/paezha/Accessibility-Food-Banks-Hamilton", subdir = "foodbanksHamilton")
  }
```

```{r load-packages, include=FALSE}
library(foodbanksHamilton) # Data package
library(patchwork)
library(sf)
library(tidyverse)
#library(tmap)
```

```{r invoke-data, include=FALSE}
data(data_da_2016)
data(dwelling_network_points_2016)
#data(hamilton_boundary)
data(population_age_income)
data(foodbank_locations)
data(modes_less40k)
data(ttm_car)
data(ttm_transit)
data(ttm_walk.RData)
```
